Supplementary material to: Drug efficacy prediction in cell lines

### 2019-01-14 docs/manuscript.Rnw
gdsc.R now reads in drug response and expression
gdsc.R includes parsing of pubchem data
new suggestions in manuscript.rnw

@@

	- what information is available on drugs (ask Oslo)

@@

	\section{Discussion}
	- empirical Bayes gives extra information via estimation of the hyper-parameters, such as informativeness of the drug information (via model for the $\gamma_d$) and relatedness of the tissues (via $\bm{\Omega}$ and $\nu$)

>>>>

	- check CTRP study

	- check data in PharamcoGx R-package

@@

	- create drug covariates from SMILES formulas with R-package rcdk.

	- try non-negative matrix factorisation/independent component analysis on binary fingerprints to get principal components that characterise the different drugs.

	- check whether compounds are PAINS \cite[]{baell_new_2010} or not. PAINS indicates whether compound is frequent false hitter.

@@

	\section{Discussion}
	- use copula's and marginal posteriors to find multivariate posteriors for contrast testing.

	- empirical Bayes gives extra information via estimation of the hyper-parameters, such as informativeness of the drug information (via model for the $\gamma_d$) and relatedness of the tissues (via $\bm{\Omega}$ and $\nu$)

### 2019-01-14 docs/supplement.Rnw
new suggestions in manuscript.rnw

  \section{Simulation setting}
  We simulate from a correctly specified model given in \ref{sec:notissuemodel}. We assume random $y_{id}$, $\x_i$, and $\bm{\beta}_d$, while we fix $\mathbf{C}$, $\gamma_d^2$, $\sigma_d^2$ and $\bm{\alpha}$. We estimate the $\bm{\mu}_d$, $\bm{\Sigma}_d$, $\delta_d$, $\bm{\alpha}$ and $\lambda$, while we fix the $\sigma_d^2$ to their true values.

>>>>

  \section{Simulation setting}
  - check model with Stan.

  - make one group of drugs and compare methods

  - use drug-specific lambda's

  - try smaller $p$ to see whether $\sigma_d^2$ become more identifiable.

  - scale-invariant instead of conjugate.

  We simulate from a correctly specified model given in \ref{sec:notissuemodel}. We assume random $y_{id}$, $\x_i$, and $\bm{\beta}_d$, while we fix $\mathbf{C}$, $\gamma_d^2$, $\sigma_d^2$ and $\bm{\alpha}$. We estimate the $\bm{\mu}_d$, $\bm{\Sigma}_d$, $\delta_d$, $\bm{\alpha}$ and $\lambda$, while we fix the $\sigma_d^2$ to their true values.
